---
title: "Reading and preparing the data"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

### Reading libraries and parameters. 

```{r, message=FALSE}
library(tidyverse)
library(quickpsy)
library(cowplot)

list.files("R", full.names = TRUE) %>% walk(source)
source("graphical_parameters.R")
source("parameters.R")
```

### Preparing the data
```{r}
dat_all <- read_csv('data/exp1.csv')  %>%
  select(subject, session, orLarge, orSmall, task, rt, response) %>%
  rename(reference = orLarge, orientation = orSmall) %>% 
  mutate(
    response = if_else(
    (reference == 0 & response == "right") |
    (reference == 90 & response == "down") |
    (reference == 180 & response == "left") |
    (reference == 270 & response == "up") |
    (response == "m"), 1, 0),
    vertical = if_else(reference == 0 | reference == 180, TRUE, FALSE),
    reference = recode(reference, `0` = "Top", `90` = "Right", 
                     `180` = "Bottom", `270` = "Left"),
    references = if_else(reference == "Top" | reference == "Right", "TR", "BL"),
    task = if_else(task == "comp", "sym", "asym"))
  
dat_all_sym <- dat_all %>% filter(task == "sym")
dat_all_asym <- dat_all %>% filter(task == "asym")
```

### Checking whether participants perform the symmetric task 

```{r fig.height=20, fig.width=7}
fit_sym_preliminar <- quickpsy(dat_all_sym, 
                      orientation, response, 
                      grouping = .(subject, reference),
                      bootstrap = "none")

ggplot() +
  facet_grid(subject ~ reference) +
  geom_point(data = fit_sym_preliminar$averages,
             aes(x = orientation, y = prob)) +
  geom_line(data = fit_sym_preliminar$curves, aes(x = x, y = y)) +
  theme_grey()
```

Participants 18, 19, 20 and 21 respond flat or reverse their responses.

### Removing participants that respond flat or reverse their responses

```{r}
dat_sym <- dat_all_sym %>% filter(!subject %in% 18:21)
```

### Checking whether participants perform the symmetric task 

```{r fig.height=20, fig.width=7}
fun_normal <- function(x, p) {
   pnorm(x, p[1] - p[2], p[3]) - pnorm(x, p[1] + p[2], p[3])
}

fit_asym_preliminar <- quickpsy(dat_all %>% filter(task == "asym"), 
                      orientation, response, 
                      fun = fun_normal,
                      parini = list(pini_origin_asym, pini_origin_asym, pini_scale),
                      grouping = .(subject, reference),
                      bootstrap = "none")

ggplot() +
  facet_grid(subject ~ reference) +
  geom_point(data = fit_asym_preliminar$averages,
             aes(x = orientation, y = prob)) +
  geom_line(data = fit_asym_preliminar$curves, aes(x = x, y = y)) +
  theme_grey()
```
Participant 17 responds flat 

### Removing participant that respond flat and the participants that could not perform the symmetric task 

```{r}

dat_sym %>% distinct(subject)
dat_asym <- dat_all %>% filter(task == "asym") %>% 
  filter(subject != 17) %>% 
  filter(task == "asym") %>% 
  semi_join(dat_sym %>% distinct(subject))

```

### Preparing the data exp 2
```{r}
dat_all2 <- read_csv('data/exp2.csv')  %>%
  select(subject, session, orLarge, orSmall, task, rt, response) %>%
  rename(reference = orLarge, orientation = orSmall) %>% 
  mutate(
    response = if_else(
    (reference == 0 & response == "right") |
    (reference == 90 & response == "down") |
    (reference == 180 & response == "left") |
    (reference == 270 & response == "up") |
    (response == "m"), 1, 0),
    vertical = if_else(reference == 0 | reference == 180, TRUE, FALSE),
    reference = recode(reference, `0` = "Top", `90` = "Right", 
                     `180` = "Bottom", `270` = "Left"),
    references = if_else(reference == "Top" | reference == "Right", "TR", "BL"),
    task = if_else(task == "comp", "sym", "asym"))


block_cond <- dat_all2 %>% 
  group_by(subject, session) %>% 
  distinct(reference) %>% 
  summarise(cond_per_block = n(), first = first(reference))
  
dat_all2 <- dat_all2 %>% left_join(block_cond)
```

### Checking whether participants perform the symmetric task in exp 2 

```{r fig.height=20, fig.width=7}
fit_sym_preliminar2 <- dat_all2 %>% 
  group_by(subject, orientation, reference, cond_per_block) %>% 
  mutate(prob = mean(response))


ggplot() +
  facet_grid(subject ~ cond_per_block) +
  geom_line(data = fit_sym_preliminar2,
             aes(x = orientation, y = prob, color = reference)) +
  theme_grey()
```

### Removing participants that respond flat or reverse their responses in exp 2

```{r}
dat2 <- dat_all2 %>% filter(!subject %in% c(14))
```
### Saving data
```{r}
save(dat_sym, file = "logdata/dat_sym.RData")
save(dat_asym, file = "logdata/dat_asym.RData")
save(dat2, file = "logdata/dat2.RData")
```

